---
title: "Summary Statistics for Eve Online in November"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Below we will use summary statistics to try and recreate some of the information shown in the Power BI Pictures folder. Datasets have been provided by CCP Quant located at https://community.eveonline.com/news/dev-blogs/monthly-economic-report-november-2016/ 

###Graphs and Code
First we will need to include the ggplot2 library

```{r}
library(ggplot2)
```


####Total ISK Destroyed by Region
This will graph the amount of ISK (In Trillions) that was destroyed. To roughly convert this into USD, $15 = 1 Billion ISK.
```{r RegionalDest, fig.width=10, fig.height=10}

RegionalStats <- read.csv("data/RegionalStats.csv") #Import the data from the csv
options("scipen"=999, "digits"=4) #stops R from using Scientific Notation when viewing ISK
regionName <- RegionalStats$regionName
totalDest <- c(RegionalStats$total.destroyed)

totalDest <- totalDest*0.000000000001 #Brings the ISK value to more viewable number (in the Trillions)

df <- data.frame(regionName, totalDest) #Creates a dataframe for use in ggplot

ggplot(data=df, aes(x=regionName, y=totalDest)) + geom_bar(fill="red3", stat="identity", linetype=2) + 
  scale_fill_hue () + 
  coord_flip() +
  theme(axis.line = element_line(color = "black", size=1, linetype="solid")) +
  labs(title = "Total ISK Destroyed by Region", y="ISK (Trillions)", x="Region") +
  scale_y_continuous(expand = c(0,0), limits = c(0,3.5))
```

####Total ISK Produced by Region
This will graph the amount of ISK (In Trillions) that was produced. To roughly convert this into USD, $15 = 1 Billion ISK.
```{r RegionalProd, fig.width=10, fig.height=10}

RegionalStats <- read.csv("data/RegionalStats.csv") #Import the data from the csv
options("scipen"=999, "digits"=4) #stops R from using Scientific Notation when viewing ISK
regionName <- RegionalStats$regionName
totalProd <- c(RegionalStats$total.production)

totalProd <- totalProd*0.000000000001 #Brings the ISK value to more viewable number (in the Trillions)

df <- data.frame(regionName, totalProd) #Creates a dataframe for use in ggplot

ggplot(data=df, aes(x=regionName, y=totalProd)) + geom_bar(fill="blue3", stat="identity", linetype=2) + 
  scale_fill_hue () + 
  coord_flip() +
  theme(axis.line = element_line(color = "black", size=1, linetype="solid")) +
  labs(title = "Total ISK Produced by Region", y="ISK (Trillions)", x="Region") +
  scale_y_continuous(expand = c(0,0), limits = c(0,30))
```